---
title: "MAB_eDCCs"
output: html_notebook
---

#Heatmap summarizing the global distribution(Fig2E)
```{r}
library(tidyverse)
library(ggplot2)
library(dplyr)

df_raw <- read.csv("Heatmap.csv")

continent_levels <- c("Asia", "Europe", "Oceania", "North America", "South America")
country_stats <- df_raw %>%
  group_by(geo_loc_name_country) %>%
  summarise(
    total_count = n(),
    continent = str_trim(first(geo_loc_name_country_continent)) 
  ) %>%
  mutate(continent = factor(continent, levels = continent_levels)) %>%
  arrange(continent, desc(total_count))
sorted_countries <- country_stats$geo_loc_name_country

df_counts <- df_raw %>%
  count(lineage, geo_loc_name_country_continent, name = "Count") %>%
  complete(lineage, geo_loc_name_country_continent, fill = list(Count = 0))

df_counts1 <- df_raw %>%
  count(lineage, geo_loc_name_country, name = "Count") %>%
  complete(lineage, geo_loc_name_country, fill = list(Count = 0))

df_counts$geo_loc_name_country_continent <- factor(df_counts$geo_loc_name_country_continent, 
                                         levels = continent_levels)
df_counts1$geo_loc_name_country <- factor(df_counts1$geo_loc_name_country, 
                                                   levels = sorted_countries)

df_counts1$Count[df_counts1$Count == 0] <- NA

desired_lineage_order <- str_sort(unique(df_counts$lineage), numeric = TRUE)

#continent
ggplot(df_counts, aes(x = geo_loc_name_country_continent, y = lineage, fill = Count)) +
  geom_tile(color = "white", lwd = 0.5) +
  coord_fixed() + 
  scale_fill_gradient(
    low = "#FFF5E1", 
    high = "#E69F00",
    trans = "log10", 
    na.value = "white", 
    breaks = c(1, 10, 100, 1000),
    labels = c("1", "10", "100", "1000")
  ) +
  scale_x_discrete(position = "top") + 
  geom_tile(color = "black", linewidth = 0.1)+
  scale_y_discrete(limits = rev(desired_lineage_order)) + 
  theme_minimal() +
  labs(title = "", x = NULL, y = "", fill = "") +
  theme(
    axis.text.x = element_text(angle = 90, hjust = 0, vjust = 0.5, size = 12, color = "black"),
    axis.text.y = element_text(size = 12, color = "black"),
    panel.border = element_rect(color = "black", fill = NA, size = 0.1),
    panel.grid = element_blank()
  ) -> p1
p1
#country
ggplot(df_counts1, aes(x = geo_loc_name_country, y = lineage, fill = Count)) +
  geom_tile(color = "white", lwd = 0.5) +
  coord_fixed() + 
  scale_fill_gradient(
    low = "#FFF5E1", 
    high = "#E69F00",
    trans = "log10", 
    na.value = "white", 
    breaks = c(1, 10, 100, 1000),
    labels = c("1", "10", "100", "1000")
  ) +
  scale_x_discrete(position = "top") + 
  geom_tile(color = "black", linewidth = 0.1)+
  scale_y_discrete(limits = rev(desired_lineage_order)) + 
  theme_minimal() +
  labs(title = "", x = NULL, y = "", fill = "") +
  theme(
    axis.text.x = element_text(angle = 90, hjust = 0, vjust = 0.5, size = 12, color = "black"),
    axis.text.y = element_text(size = 12, color = "black"),
    panel.border = element_rect(color = "black", fill = NA, size = 0.1),
    panel.grid = element_blank()
  ) -> p2
p2
```

#DCCs and eDCCs expansion boxplot(Fig3A)
```{r}
read.csv("expansion_boxplot.csv")->df
library(ggplot2)
df$Type <- factor(df$Type, levels = c("DCC1","DCC2","DCC3","DCC4","DCC5","DCC6","DCC7",
                                    "eDCC8","eDCC9","eDCC10","eDCC11","eDCC12","eDCC13","eDCC14",
                                    "eDCC15","eDCC16","eDCC17","eDCC18","eDCC19","eDCC20",
                                    "eDCC21","eDCC22","eDCC23","eDCC24","eDCC25","eDCC26","eDCC27",
                                    "eDCC28","eDCC29","eDCC30","eDCC31","eDCC32","eDCC33","eDCC34",
                                    "eDCC35","eDCC36","eDCC37","eDCC38"))
p1<-ggplot(df, aes(
  x = Type,
  y = median_time,
  color = Type1,
  size = strains
)) +
  #geom_point(alpha = 0.99) +
  geom_errorbar(aes(ymin = low, ymax = up), size = 1, width = 0) +  
  geom_point(aes(color = Type1, fill = Type1), shape = 21, stroke = 1,size =4) +  
  #geom_linerange(aes(ymin = low, ymax = up), linewidth = 0.9, alpha = 0.8) +
  scale_color_manual(values = c("#AA77CC","#437DBB")) +
  scale_fill_manual(values = c("#E9D5F8","#BDD1E8")) +
  #scale_size_continuous(range = c(2, 9)) +
  ylim(1840,2020)+
  theme_classic() +
  labs(x = "", y = "Expansion time", title = "") +
  theme(
    axis.text.x = element_text(size = 10, color = "black",angle = 45,hjust = 1),
    axis.text.y = element_text(size = 10, color = "black"),
    axis.title.x = element_text(size = 10, color = "black"),
    legend.position = "none",
    strip.text = element_text(size = 10),
    axis.title.y = element_text(size = 10, color = "black"),
    axis.line = element_line(size = 0.5, colour = "black"),
    axis.ticks = element_line(size = 0.5, colour = "black"),
    axis.ticks.length = unit(0.3, "cm")
  ) 

origin_df <- data.frame(
  Type = c("DCC1","DCC2","DCC3","DCC4","DCC5","DCC6","DCC7",
           "eDCC8","eDCC9","eDCC10","eDCC11","eDCC12","eDCC13","eDCC14",
           "eDCC15","eDCC16","eDCC17","eDCC18","eDCC19","eDCC20",
           "eDCC21","eDCC22","eDCC23","eDCC24","eDCC25","eDCC26","eDCC27",
           "eDCC28","eDCC29","eDCC30","eDCC31","eDCC32","eDCC33","eDCC34",
           "eDCC35","eDCC36","eDCC37","eDCC38"),
  year = c(1862,1860,1846,1985,1975,1949,1958,
           1939,1955,1991,1960,1940,1927,1956,
           1994,1980,1979,2012,2006,1987,
           1975,1975,1962,1995,1925,2008,
           1954,1969,2006,1983,1977,1993,2014,
           2007,1997,2009,2014,2007)
)

origin_df$Type1 <- ifelse(grepl("^eDCC", origin_df$Type), "eDCC", "DCC")

p1 <- p1 +
  geom_text(
    data = origin_df,
    aes(x = Type, y = year),
    label = "\u2605",              
    family = "Arial Unicode MS", 
    colour = "darkgrey",
    size = 4.5
  )

p1 <- p1 +
  geom_vline(
    xintercept = 7.5,
    linetype = "dashed",
    linewidth = 0.6,
    colour = "grey30"
  ) 

p1 
```

#BEAST skyline(Fig3B)
```{r}
#DCC1-3
library(ggplot2)
library(dplyr)
library(tidyr)
df <- read.csv(
  "DCC1-3.csv",
  header = TRUE,
  stringsAsFactors = FALSE
)

dcc_levels <- paste0("DCC", 1:3)
df <- df[df$Type %in% dcc_levels, ]
df$Type <- factor(df$Type, levels = dcc_levels)
dcc_cols <- c(
  "DCC1" = "#E3B48C",  
  "DCC2" = "#3FA38E",
  "DCC3" = "#437DBB")
mean_trend <- df %>%
  group_by(Year_Round = round(year)) %>%
  summarise(
    mean_median = mean(mean, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  filter(Year_Round <= 2020)

ggplot(df, aes(x = year, y = median, color = Type, group = Type)) +
  geom_line(linewidth = 1, alpha = 0.5) +
  geom_smooth(
    data = mean_trend,
    aes(x = Year_Round, y = mean_median),
    method = "loess",
    span = 0.25,       
    se = FALSE,
    color = "black",
    linewidth = 1.3,
    inherit.aes = FALSE
  )+
  theme_bw() + 
  scale_y_log10(name="Effective Population Size",
                labels = c(expression(1%*%10^5),
                           expression(1%*%10^6),
                           expression(1%*%10^7),
                           expression(1%*%10^8)),
                #expand = c(0,0),
                breaks = c(1E+05, 1E+06, 1e+07, 80000000),
                limits = c(100000, 80000000))+
  scale_color_manual(values = dcc_cols) +
  theme_classic() +
  theme(
    legend.position = "right",
    axis.text.x = element_text(size = 23,color="black"),
    axis.text.y = element_text(size = 23,color="black"),
    axis.title = element_blank(),
    axis.line = element_line(size = 1, colour = "black"),
    axis.ticks = element_line(size = 1, colour = "black"),
    axis.ticks.length = unit(0.3, "cm")
  )->p1
p1

#DCC4-7
df <- read.csv(
  "DCC4-7.csv",
  header = TRUE,
  stringsAsFactors = FALSE
)

dcc_levels <- paste0("DCC", 4:7)
df <- df[df$Type %in% dcc_levels, ]
df$Type <- factor(df$Type, levels = dcc_levels)
dcc_cols <- c(
  "DCC4" = "#E3B48C",
  "DCC5" = "#AF96C0",  
  "DCC6" = "#3FA38E",
  "DCC7" = "#437DBB")
mean_trend <- df %>%
  group_by(Year_Round = round(year)) %>%
  summarise(
    mean_median = mean(mean, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  filter(Year_Round <= 2020)

ggplot(df, aes(x = year, y = median, color = Type, group = Type)) +
  geom_line(linewidth = 1, alpha = 0.5) +
  geom_smooth(
    data = mean_trend,
    aes(x = Year_Round, y = mean_median),
    method = "loess",
    span = 0.25,      
    se = FALSE,
    color = "black",
    linewidth = 1.3,
    inherit.aes = FALSE
  )+
  theme_bw() + 
  scale_y_log10(name="Effective Population Size",
                labels = c(expression(1%*%10^5),
                           expression(1%*%10^6),
                           expression(1%*%10^7),
                           expression(1%*%10^8)),
                #expand = c(0,0),
                breaks = c(1E+05, 1E+06, 1e+07, 80000000),
                limits = c(100000, 80000000))+
  scale_color_manual(values = dcc_cols) +
  theme_classic() +
  scale_x_continuous(name="Year",limits=c(1880, 2018),breaks = seq(1880, 2020, by = 40)) + 
  theme(
    legend.position = "right",
    axis.text.x = element_text(size = 23,color="black"),
    axis.text.y = element_text(size = 23,color="black"),
    axis.title = element_blank(),
    axis.line = element_line(size = 1, colour = "black"),
    axis.ticks = element_line(size = 1, colour = "black"),
    axis.ticks.length = unit(0.3, "cm")
  )->p2
p2

#eDCC
df <- read.csv(
  "eDCC1-7.csv",
  header = TRUE,
  stringsAsFactors = FALSE
)

dcc_levels <- c(paste0("eDCC", 8:14), "eDCC31")
df <- df[df$Type %in% dcc_levels, ]
df$Type <- factor(df$Type, levels = dcc_levels)
dcc_cols <- c(
  "eDCC8"  = "#E3B48C",
  "eDCC9"  = "#F3CFC6",
  "eDCC10" = "#3FA38E",  
  "eDCC11" = "#8DAAD6",
  "eDCC12" = "#AF96C0",
  "eDCC13" = "#6FAFB7",
  "eDCC14" = "#C6DCF2",
  "eDCC31" = "#437DBB"
)
mean_trend <- df %>%
  group_by(Year_Round = round(year)) %>%
  summarise(
    mean_median = mean(mean, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  filter(Year_Round <= 2020)

ggplot(df, aes(x = year, y = median, color = Type, group = Type)) +
  geom_line(linewidth = 1, alpha = 0.5) +
  geom_smooth(
    data = mean_trend,
    aes(x = Year_Round, y = mean_median),
    method = "loess",
    span = 0.25,      
    se = FALSE,
    color = "black",
    linewidth = 1.3,
    inherit.aes = FALSE
  )+
  scale_x_continuous(name="Year",limits=c(1880, 2018),breaks = seq(1880, 2020, by = 40)) + 
  theme_bw() + 
  scale_y_log10(name="Effective Population Size",
                labels = c(expression(1%*%10^5),
                           expression(1%*%10^6),
                           expression(1%*%10^7),
                           expression(5%*%10^7)),
                #expand = c(0,0),
                breaks = c(1E+05, 1E+06, 1e+07, 50000000),
                limits = c(100000, 30000000))+
  scale_color_manual(values = dcc_cols) +
  theme_classic() +
  theme(
    legend.position = "right",
    axis.text.x = element_text(size = 23,color="black"),
    axis.text.y = element_text(size = 23,color="black"),
    axis.title = element_blank(),
    axis.line = element_line(size = 1, colour = "black"),
    axis.ticks = element_line(size = 1, colour = "black"),
    axis.ticks.length = unit(0.3, "cm")
  )->p3
p3
```

#Population size and time regression(Fig3C and FigS5A-D)
```{r}
#Fig3C
library(ggplot2)
library(ggExtra)
read.csv("year_median.csv")->df
fit <- lm(log ~ time, df)
coefficients <- coef(fit)
intercept <- coefficients[1]
slope <- coefficients[2]
r_squared <- summary(fit)$r.squared
p_value <- summary(fit)$coefficients[2, 4]
df$Type <- factor(df$Type, levels = c("DCC", "eDCC"))
scatter_plot <- ggplot(df, aes(x = time, y = log, color =Type)) +
  geom_point(size = df$log*12,shape =21,aes(color =Type),stroke = 0.5,
             fill = alpha(c("#AA77CC","#437DBB")[as.numeric(df$Type)], 0.6),) +
  scale_color_manual(values = c("#AA77CC","#437DBB")) +
  scale_fill_manual(values = c("#AA77CC","#437DBB")) + 
  geom_smooth(method = "lm", se = TRUE, color = "black",linewidth = 1,linetype = "dashed",) +
  labs(x = "Time before present (years)", y = "Population Size(log10)") +
  #scale_x_continuous(limits = c(1935,2025),breaks=c(seq(1900,2030, by=20))) +
  theme_bw() +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 1.5),  
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(), 
    axis.text.x = element_text(size = 24, color = "black"),
    axis.text.y = element_text(size = 24, color = "black"),
    axis.title.x = element_text(size = 24, color = "black"),
    legend.position = "none",
    strip.text = element_text(size = 24),
    axis.title.y = element_text(size = 24, color = "black")) 
scatter_plot
p <- scatter_plot +
  annotate("text", x = 29, y = max(df$log) - 0.2, 
           label = paste0("R² = ", round(r_squared, 2), ", p < 0.001 "),size = 8,color = "black") 
a<- ggMarginal(p, type = "density", groupColour = F,groupFill = T, alpha =0.7,margins = "both", size = 3.5) 
p

#FigS5A
read.csv("TRL_filter_maha.csv")->df

library(ggplot2)
library(ggpubr)
library(ggExtra)
fit <- lm(log ~ Year, df)

coefficients <- coef(fit)
intercept <- coefficients[1]
slope <- coefficients[2]
r_squared <- summary(fit)$r.squared
p_value <- summary(fit)$coefficients[2, 4]

scatter_plot <- ggplot(df, aes(x = Year, y = log,color =Type)) +
  geom_point(size = df$log*6,alpha =0.9,shape =21,color ="white",aes(fill =Type),stroke = 0.5) +
  scale_fill_manual(values = c("#ED7545","#1F4D85")) + 
  scale_color_manual(values = c("#ED7545","#1F4D85")) +
  geom_smooth(method = "lm", se = TRUE, color = "black",linewidth = 1,linetype = "dashed",) +
  labs(x = "Estimated Age (Year)", y = "Population Size(log10)") +
  #scale_x_continuous(limits = c(1935,2025),breaks=c(seq(1900,2030, by=20))) +
  theme_bw() +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 1.2),  
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),  
    axis.text.x = element_text(size = 40, color = "black"),
    axis.text.y = element_text(size = 40, color = "black"),
    axis.title.x = element_text(size = 40, color = "black"),
    legend.position = "none",
    strip.text = element_text(size = 40),
    axis.title.y = element_text(size = 40, color = "black")) 

scatter_plot

p <- scatter_plot +
  annotate("text", x = max(df$Year)-21, y = max(df$log) - 2.4, 
           label = paste0("R² = ", round(r_squared, 2), ", p < 0.001 "),size = 12,color = "black") +
  annotate("text", x = max(df$Year)-21, y = max(df$log) - 2.1, 
           label = paste0("Different Mutation Rate"),size = 12,color = "black")


#FigS5B-D
#USA
read.csv("all_TRL_USA.csv")->df
library(ggplot2)
library(ggpubr)
library(ggExtra)
fit <- lm(log ~ Year, df)

coefficients <- coef(fit)
intercept <- coefficients[1]
slope <- coefficients[2]
r_squared <- summary(fit)$r.squared
p_value <- summary(fit)$coefficients[2, 4]

scatter_plot <- ggplot(df, aes(x = Year, y = log,color =Type)) +
  geom_point(size = df$log*6,alpha =0.9,shape =21,color ="white",aes(fill =Type),stroke = 0.5) +
  scale_fill_manual(values = c("#ED7545","#1F4D85")) + 
  scale_color_manual(values = c("#ED7545","#1F4D85")) +
  geom_smooth(method = "lm", se = TRUE, color = "black",linewidth = 1,linetype = "dashed",) +
  labs(x = "Estimated Age (Year)", y = "Population Size(log10)") +
  #scale_x_continuous(limits = c(1935,2025),breaks=c(seq(1900,2030, by=20))) +
  theme_bw() +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 1.2),  
    panel.grid.major = element_blank(),  
    panel.grid.minor = element_blank(),  
    axis.text.x = element_text(size = 40, color = "black"),
    axis.text.y = element_text(size = 40, color = "black"),
    axis.title.x = element_text(size = 40, color = "black"),
    legend.position = "none",
    strip.text = element_text(size = 40),
    axis.title.y = element_text(size = 40, color = "black")) 

scatter_plot

p <- scatter_plot +
  annotate("text", x = max(df$Year)-21, y = max(df$log) - 2.4, 
           label = paste0("R² = ", round(r_squared, 2), ", p < 0.001 "),size = 12,color = "black") +
  annotate("text", x = max(df$Year)-21, y = max(df$log) - 2.1, 
           label = paste0("USA"),size = 12,color = "black")

#UK
read.csv("all_TRL_UK.csv")->df
library(ggplot2)
library(ggpubr)
library(ggExtra)
fit <- lm(log ~ Year, df)

coefficients <- coef(fit)
intercept <- coefficients[1]
slope <- coefficients[2]
r_squared <- summary(fit)$r.squared
p_value <- summary(fit)$coefficients[2, 4]

scatter_plot <- ggplot(df, aes(x = Year, y = log,color =Type)) +
  geom_point(size = df$log*6,alpha =0.9,shape =21,color ="white",aes(fill =Type),stroke = 0.5) +
  scale_fill_manual(values = c("#ED7545","#1F4D85")) + 
  scale_color_manual(values = c("#ED7545","#1F4D85")) +
  geom_smooth(method = "lm", se = TRUE, color = "black",linewidth = 1,linetype = "dashed",) +
  labs(x = "Estimated Age (Year)", y = "Population Size(log10)") +
  #scale_x_continuous(limits = c(1935,2025),breaks=c(seq(1900,2030, by=20))) +
  theme_bw() +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 1.2),  
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),  
    axis.text.x = element_text(size = 40, color = "black"),
    axis.text.y = element_text(size = 40, color = "black"),
    axis.title.x = element_text(size = 40, color = "black"),
    legend.position = "none",
    strip.text = element_text(size = 40),
    axis.title.y = element_text(size = 40, color = "black")) 

scatter_plot

p <- scatter_plot +
  annotate("text", x = max(df$Year)-21, y = max(df$log) - 2.4, 
           label = paste0("R² = ", round(r_squared, 2), ", p < 0.001 "),size = 12,color = "black") +
  annotate("text", x = max(df$Year)-21, y = max(df$log) - 2.1, 
           label = paste0("UK"),size = 12,color = "black")

#AS
read.csv("all_TRL_AS.csv")->df
library(ggplot2)
library(ggpubr)
library(ggExtra)
fit <- lm(log ~ Year, df)

coefficients <- coef(fit)
intercept <- coefficients[1]
slope <- coefficients[2]
r_squared <- summary(fit)$r.squared
p_value <- summary(fit)$coefficients[2, 4]

scatter_plot <- ggplot(df, aes(x = Year, y = log,color =Type)) +
  geom_point(size = df$log*6,alpha =0.9,shape =21,color ="white",aes(fill =Type),stroke = 0.5) +
  scale_fill_manual(values = c("#ED7545","#1F4D85")) + 
  scale_color_manual(values = c("#ED7545","#1F4D85")) +
  geom_smooth(method = "lm", se = TRUE, color = "black",linewidth = 1,linetype = "dashed",) +
  labs(x = "Estimated Age (Year)", y = "Population Size(log10)") +
  #scale_x_continuous(limits = c(1935,2025),breaks=c(seq(1900,2030, by=20))) +
  theme_bw() +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 1.2),  
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),  
    axis.text.x = element_text(size = 40, color = "black"),
    axis.text.y = element_text(size = 40, color = "black"),
    axis.title.x = element_text(size = 40, color = "black"),
    legend.position = "none",
    strip.text = element_text(size = 40),
    axis.title.y = element_text(size = 40, color = "black")) 

scatter_plot

p <- scatter_plot +
  annotate("text", x = max(df$Year)-21, y = max(df$log) - 2.4, 
           label = paste0("R² = ", round(r_squared, 2), ", p < 0.001 "),size = 12,color = "black") +
  annotate("text", x = max(df$Year)-21, y = max(df$log) - 2.1, 
           label = paste0("Australia"),size = 12,color = "black")

#bryant-TRl
data <- read.csv("TRL_bryant.csv")
boxplot_stats <- data %>%
  group_by(Subtype) %>%
  summarize(
    Mean = mean(TRL),
    MAX= max(TRL),
    Q1 = quantile(TRL, 0.25),
    Q3 = quantile(TRL, 0.75),
    Upper = max(TRL),
    Lower = min(TRL)
  )
write.csv(boxplot_stats,"bryant_TRL.csv")

read.csv("bryant_TRL.csv")->df
library(ggplot2)
library(ggpubr)
library(ggExtra)
fit <- lm(log ~ Year, df)

coefficients <- coef(fit)
intercept <- coefficients[1]
slope <- coefficients[2]
r_squared <- summary(fit)$r.squared
p_value <- summary(fit)$coefficients[2, 4]

scatter_plot <- ggplot(df, aes(x = Year, y = log,color =Type)) +
  geom_point(size = df$log*6,alpha =0.8,shape =21,color ="white",aes(fill =Type),stroke = 0.5) +
  scale_fill_manual(values = c("#ED7545","#1F4D85")) + 
  scale_color_manual(values = c("#ED7545","#1F4D85")) +
  geom_smooth(method = "lm", se = TRUE, color = "black",linewidth = 1,linetype = "dashed",) +
  labs(x = "Estimated Age (Year)", y = "Population Size(log10)") +
  #scale_x_continuous(limits = c(1935,2025),breaks=c(seq(1900,2030, by=20))) +
  theme_bw() +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 1.2),  
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),  
    axis.text.x = element_text(size = 40, color = "black"),
    axis.text.y = element_text(size = 40, color = "black"),
    axis.title.x = element_text(size = 40, color = "black"),
    legend.position = "none",
    strip.text = element_text(size = 40),
    axis.title.y = element_text(size = 40, color = "black")) 

scatter_plot

p <- scatter_plot +
  annotate("text", x = max(df$Year)-45, y = max(df$log) - 2.7, 
           label = paste0("R² = ", round(r_squared, 2), ", p < 0.001 "),size = 12,color = "black") +
  annotate("text", x = max(df$Year)-45, y = max(df$log) - 2.5, 
           label = paste0("Multicenter"),size = 12,color = "black")

```

#lineage heatmap(Fig4A-B)
```{r}
#Fig4A
library(dplyr)
library(tidyr)
library(stringr)
df <- read.csv("all_evolution_pathway.csv", header = TRUE)

df_mean <- df %>%
  mutate(match = as.numeric(str_remove(match, "%"))) %>%
  group_by(tree_name, CC_type) %>%
  summarise(
    mean_match = mean(match, na.rm = TRUE),
    .groups = "drop"
  )
tree_order <- c("eDCC33","eDCC37","DCC7","eDCC32","eDCC30","eDCC36","eDCC35","DCC6",
                "eDCC31","DCC3","eDCC34","eDCC38","eDCC28","eDCC25","DCC4","eDCC10",
                "DCC2","eDCC9","DCC1","eDCC16","eDCC27","eDCC29","eDCC12","eDCC8",
                "eDCC23","eDCC19","eDCC13","eDCC24","eDCC11","eDCC22","eDCC18","eDCC20",
                "eDCC26","eDCC15","DCC5","eDCC21","eDCC17","eDCC14","NonDCC")

cc_order <- c("eDCC33","eDCC37","DCC7","eDCC32","eDCC30","eDCC36","eDCC35","DCC6",
                "eDCC31","DCC3","eDCC34","eDCC38","eDCC28","eDCC25","DCC4","eDCC10",
                "DCC2","eDCC9","DCC1","eDCC16","eDCC27","eDCC29","eDCC12","eDCC8",
                "eDCC23","eDCC19","eDCC13","eDCC24","eDCC11","eDCC22","eDCC18","eDCC20",
                "eDCC26","eDCC15","DCC5","eDCC21","eDCC17","eDCC14")

tree_strains <- df %>%
  group_by(tree_name) %>%
  summarise(Strains = max(Strains, na.rm = TRUE)) %>%  
  mutate(tree_label = paste0(tree_name, " (", Strains, ")"))  
tree_labels_ordered <- tree_strains %>%
  filter(tree_name %in% tree_order) %>%
  arrange(factor(tree_name, levels = tree_order)) %>%
  pull(tree_label)

cc_order_markers <- paste0(cc_order, "_DefiningSNPs")

df_plot <- expand.grid(
  tree_name = tree_order,
  CC_type   = rev(cc_order_markers)
) %>%
  left_join(df_mean, by = c("tree_name", "CC_type")) %>%
  left_join(tree_strains, by = "tree_name") %>%
  mutate(
    tree_label = factor(tree_label, levels = rev(tree_labels_ordered)),  
    CC_type   = factor(CC_type, levels = cc_order_markers),
    mean_match = ifelse(is.na(mean_match), NA, mean_match)
  )
library(ggplot2)

p1 <- ggplot(
  df_plot,
  aes(x = CC_type, y = tree_label, fill = mean_match)
) +
  coord_fixed() +
  scale_fill_gradientn(
    colours = c("white", "#1B7F79"),
    values  = c(0, 1),
    breaks  = c(0, 25, 50, 75, 100),
    labels  = c("0", "25", "50", "75", "100"),
    na.value = "#BFBFBF",
    name = "Mean match (%)"
  )+
  scale_x_discrete(position = "top") +
  
  theme_minimal(base_size = 12) +
  labs(
    x = NULL,
    y = NULL
  ) +
  geom_tile(color = "black", linewidth = 0.1)+
  theme(
    axis.text.x = element_text(
      angle = 45,
      hjust = 0,
      vjust = 0,
      color = "black",
      size = 7
    ),
    axis.text.y = element_text(
      color = "black",
      size = 8
    ),
    panel.grid = element_blank(),
    panel.border = element_rect(
      colour = "black",
      fill = NA,
      linewidth = 0.5
    ),
    legend.position = "right"
  )
p1

#Fig4B
df <- read.csv("all_match.csv", header = TRUE, stringsAsFactors = FALSE)
df$Type<- ifelse(grepl("^eDCC", df$tree_name), "eDCC", "DCC")
sample_order <- c(
  paste0("DCC", 1:7),
  paste0("eDCC", 8:38)
)
df$tree_name<- factor(df$tree_name, levels = sample_order)

library(ggplot2)

p2 <- ggplot(df, aes(x = tree_name, y = match_per, color = Type, fill = Type)) +
  stat_boxplot(aes(colour = Type), geom = "errorbar", width = 0.2, linewidth = 0.4) +
  geom_boxplot(outlier.shape = NA, linewidth = 0.6, alpha = 1, fill = "white", width = 0.4) +
  geom_boxplot(aes(colour = Type), outlier.shape = NA, linewidth = 0.3, fill = "white", alpha = 1, width = 0.4) +
  #geom_boxplot(aes(colour = Type1,fill =Type1),outlier.shape = NA,linewidth =0.2,,alpha =0.3,width =0.4) +
  geom_jitter(size = 0.8,fill = alpha(c("#AA77CC","#437DBB")[as.numeric(as.factor(df$Type))], 0.4),shape = 21, stroke = 0.5, width = 0.18) +
  
  scale_color_manual(values = c("#AA77CC","#437DBB")) +
  scale_fill_manual(values = c("#AA77CC","#437DBB")) +
  theme_classic() +
  labs(x = "", y = "Match percentage", title = "") +
  theme(
    axis.text.x = element_text(size = 11, color = "black",angle = 45,hjust = 1),
    axis.text.y = element_text(size = 11, color = "black"),
    axis.title.x = element_text(size = 11, color = "black"),
    legend.position = "none",
    strip.text = element_text(size = 11),
    axis.title.y = element_text(size = 11, color = "black"),
    axis.line = element_line(size = 1, colour = "black"),
    axis.ticks = element_line(size = 1, colour = "black"),
    axis.ticks.length = unit(0.3, "cm")
  ) 
p2

```

# Gene positive selection in MAB(Fig5A-B)
```{r}
library(ggplot2)
library(dplyr)
library(scatterpie)
library(patchwork) 
library(tidyr) 
#DCC
data <- read.csv("positive_selection.csv") 
data$Total <- data$NS + data$S
gene_sum_order <- data %>%
  group_by(gene) %>%
  summarise(GrandTotal = sum(Total)) %>%
  arrange(desc(GrandTotal)) 
sorted_genes <- gene_sum_order$gene
plot_data <- data %>% filter(Total > 0)
plot_data$gene <- factor(plot_data$gene, levels = sorted_genes)
plot_data$type <- factor(plot_data$type, levels = c("eDCC31","eDCC14","eDCC13","eDCC12","eDCC11","eDCC10","eDCC9","eDCC8","DCC7","DCC6","DCC5","DCC4","DCC3","DCC2","DCC1"))

plot_data$x_num <- as.numeric(plot_data$gene)
plot_data$y_num <- as.numeric(plot_data$type)

max_radius_size <- 0.48 
threshold <- 30   
min_radius <- 0.15 

plot_data$radius <- min_radius +
  (sqrt(pmin(plot_data$Total, threshold)) / sqrt(threshold)) *
  (max_radius_size - min_radius)
ggplot() +
  geom_scatterpie(data = plot_data, 
                  aes(x = x_num, y = y_num, r = radius),
                  cols = c("NS", "S"), 
                  color = "white", 
                  size =0,
                  alpha = 1) +
  coord_fixed() +
  scale_x_continuous(breaks = 1:length(levels(plot_data$gene)), 
                     labels = levels(plot_data$gene),
                     position = "top",
                     expand = c(0, 0.1) ) + 
  scale_y_continuous(
    breaks = 1:length(levels(plot_data$type)), 
    labels = levels(plot_data$type),
    expand = c(0, 0.6)
  ) +
  scale_fill_manual(values = c("NS" = "#7BADB5", "S" = "#DBB590"),
                    name = "Mutation Type") +
  theme_minimal(base_size = 14) + 
  theme(
    panel.grid = element_blank(),
    axis.title = element_blank(),
    axis.text.x.top = element_text(angle = 90, vjust = 0.1, hjust = 1, 
                                   size = 6, color = "black"),
    axis.text.y = element_text(size = 6, color = "black"),
    legend.position = "",
    plot.margin = margin(t = 5, r = 5, b = 0, l = 5)
  ) ->p1
p1

bar_data <- data %>%
  group_by(gene) %>%
  summarise(NS = sum(NS), S = sum(S)) %>%
  pivot_longer(cols = c("NS", "S"), names_to = "Mutation_Type", values_to = "Count")

bar_data$gene <- factor(bar_data$gene, levels = sorted_genes)
bar_data$x_num <- as.numeric(bar_data$gene)
bar_data$Mutation_Type <- factor(bar_data$Mutation_Type, levels = c("S","NS"))

p2 <- ggplot(bar_data, aes(x = x_num, y = Count, fill = Mutation_Type)) +
  geom_bar(stat = "identity", width = 0.7) + # width 控制柱子宽度，0.7 比较美观
  
  scale_fill_manual(values = c("NS" = "#7BADB5", "S" = "#DBB590"), 
                    name = "Mutation Type") +

  scale_x_continuous(
    expand = c(0, 0.1),
    breaks = 1:length(levels(bar_data$gene)),
    labels = NULL 
  ) +
  
  scale_y_continuous(
    expand = c(0, 0.6) 
  ) +
  
  theme_minimal(base_size = 14) +
  labs(y = "") +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid = element_blank(),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(), 
    axis.line.y = element_line(color = "black", size = 0.3),
    axis.ticks.y = element_line(color = "black", size = 0.3),
    axis.text.y = element_text(color = "black",size = 6),
    plot.margin = margin(t = -2, r = 5, b = 10, l = 5),
    legend.position = ""    
  )
p2

combined_plot <- p1 / p2 + plot_layout(heights = c(4, 2))

print(combined_plot)

#IGR
library(ggplot2)
library(dplyr)
library(scatterpie)
library(tidyr)    
library(tidyverse)

data <- read.csv("IGR.csv")
gene_sum_order <- data %>%
  group_by(IGR) %>%
  summarise(GrandTotal = sum(count)) %>%
  arrange(desc(GrandTotal))
gene_sum_order$IGR <- factor(gene_sum_order$IGR, levels = gene_sum_order$IGR)

p3 <- ggplot(gene_sum_order, aes(x = IGR, y = GrandTotal)) +
  geom_col(width = 0.7, fill = "#9A8FB5") +  
  scale_y_continuous(expand = expansion(mult = c(0, 0.05))) +
  theme_minimal(base_size = 14) +
  labs(y = "") +
  theme(
    panel.grid = element_blank(),
    axis.title.x = element_blank(),
    axis.text.x = element_text(angle = 30, hjust = 1, vjust = 1, size = 10, color = "black"), 
    axis.line.y = element_line(color = "black", size = 0.5),
    axis.ticks.y = element_line(color = "black", size = 0.5),
    axis.line.x = element_line(color = "black", size = 0.5),  
    axis.text.y = element_text(color = "black", size = 11),
    plot.margin = margin(t = 5, r = 5, b = 10, l = 20),
    legend.position = "none"
  )

p3
```

#Host status, subspecies distribution, sample source bar graph(FigS1A-C)
```{r}
#Host status
library(ggplot2)
data <- data.frame(
  Type = c("CF", "Non-CF"),
  Count = c(1495, 410)
)
data$Percentage <- data$Count / sum(data$Count) * 100
data$Type = factor(data$Type, levels=c("CF", "Non-CF"))
colors <- c("#456FBB","#61ACA2", "#F0C96E")
p1 <- ggplot(data, aes(x = Type, y = Percentage, fill = Type)) +
  geom_bar(stat = "identity", color = "black",alpha =1,width = 0.7) +
  geom_text(aes(label = sprintf("%.1f%%", Percentage)), vjust = -0.5,size = 10) +
  scale_fill_manual(values = colors) +
  scale_y_continuous(expand = c(0, 0),limits = c(0,88)) +
  labs(x = "",
       y = "Percentage") +
  theme_classic() +
  theme(#axis.text.x = element_text(size = 28,color="black"),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 28,color="black"),
    axis.title.x = element_text(size = 15,color="black"),
    axis.title.y = element_text(size = 28,color="black"),
    legend.position = "",
    axis.line.x = element_line(color = "black", size = 1.2), 
    axis.line.y = element_line(color = "black", size = 1.2),  
    axis.ticks.length = unit(0.1, "cm"), 
    axis.ticks = element_line(color = "black", size = 1.2),
    panel.spacing.x = unit(0, "pt")) 
p1

#Subspecies distribution
library(ggplot2)
data <- data.frame(
  Type = c("ABS", "MAS", "BOL"),
  Count = c(6596, 2417, 506)
)
data$Percentage <- data$Count / sum(data$Count) * 100
data$Type = factor(data$Type, levels=c("ABS", "MAS", "BOL"))
colors <- c("#456FBB","#61ACA2", "#F0C96E")
p2 <- ggplot(data, aes(x = Type, y = Percentage, fill = Type)) +
  geom_bar(stat = "identity", color = "black",alpha =1,width = 0.7) +
  geom_text(aes(label = sprintf("%.1f%%", Percentage)), vjust = -0.5,size = 10) +
  scale_fill_manual(values = colors) +
  scale_y_continuous(expand = c(0, 0),limits = c(0,79)) +
  labs(x = "",
       y = "Percentage") +
  theme_classic() +
  theme(#axis.text.x = element_text(size = 28,color="black"),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 28,color="black"),
    axis.title.x = element_text(size = 15,color="black"),
    axis.title.y = element_text(size = 28,color="black"),
    legend.position = "",
    axis.line.x = element_line(color = "black", size = 1.2), 
    axis.line.y = element_line(color = "black", size = 1.2), 
    axis.ticks.length = unit(0.1, "cm"), 
    axis.ticks = element_line(color = "black", size = 1.2),
    panel.spacing.x = unit(0, "pt")) 
p2

#Sample source 
library(ggplot2)
data <- data.frame(
  Type = c("IPS","EPS","ENS"),
  Count = c(2341, 312, 46)
)
data$Percentage <- data$Count / sum(data$Count) * 100
data$Type = factor(data$Type, levels=c("IPS","EPS","ENS"))
colors <- c("#456FBB","#61ACA2", "#F0C96E")
p3 <- ggplot(data, aes(x = Type, y = Percentage, fill = Type)) +
  geom_bar(stat = "identity", color = "black",alpha =1,width = 0.7) +
  geom_text(aes(label = sprintf("%.1f%%", Percentage)), vjust = -0.5,size = 10) +
  scale_fill_manual(values = colors) +
  scale_y_continuous(expand = c(0, 0),limits = c(0,95)) +
  labs(x = "",
       y = "Percentage") +
  theme_classic() +
  theme(#axis.text.x = element_text(size = 28,color="black"),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 28,color="black"),
        axis.title.x = element_text(size = 15,color="black"),
        axis.title.y = element_text(size = 28,color="black"),
        legend.position = "",
        axis.line.x = element_line(color = "black", size = 1.2), 
        axis.line.y = element_line(color = "black", size = 1.2), 
        axis.ticks.length = unit(0.1, "cm"), 
        axis.ticks = element_line(color = "black", size = 1.2),
        panel.spacing.x = unit(0, "pt")) 
p3

```

#Rarefaction(FigS1D-E)
```{r}
library(dplyr)
library(ggplot2)

results <- read.csv("eDCC_subsamples_repeated.csv")

summary_results <- results %>%
  group_by(SampleSize) %>%
  summarize(
    AvgRepeatedValuesCount = mean(RepeatedValuesCount),
    Avgper = mean(Per)
  )

ggplot(results, aes(x = factor(SampleSize))) +
  geom_boxplot(aes(y = RepeatedValuesCount), fill = "#3A845D",color = "#3A845D", alpha = 0.5, width = 0.3) +
  geom_boxplot(aes(y = Per * max(results$RepeatedValuesCount) / max(results$Per)), fill = "#5043A4",color = "#5043A4", alpha = 0.5, width = 0.3) +
  geom_smooth(aes(y = RepeatedValuesCount, group = 1), method = "loess", se = TRUE, linetype = "solid", color = "#3A845D",linewidth = 1.3) +
  geom_smooth(aes(y = Per * max(results$RepeatedValuesCount) / max(results$Per), group = 1), 
              method = "loess", se = TRUE, linetype = "solid", color = "#5043A4",linewidth = 2) +
  scale_y_continuous(
    name = "Number of Cluster Counts",
    sec.axis = sec_axis(~ . * max(results$Per) / max(results$RepeatedValuesCount), 
                        name = "Percentage of Uncluster Values")
  ) +
  theme_bw() +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 1.2),  
    #panel.grid.major = element_blank(),  
    panel.grid.minor = element_blank(), 
    axis.text.x = element_text(size = 26, color = "black"),
    axis.text.y = element_text(size = 26, color = "black"),
    axis.title.x = element_text(size = 26, color = "black"),
    legend.position = "none",
    strip.text = element_text(size = 26),
    axis.title.y = element_text(size = 26, color = "black"),
    plot.margin = margin(1, 1, 1, 1, "cm")) +
  labs(title = "",
       x = "Sample Size") -> plot

print(plot)
```

#Recombination patterns of clade-defining SNPs(FigS7)
```{r}
#ABS
library(tidyverse)

type_df <- read.csv("../ABS_type.csv", stringsAsFactors = FALSE)
colnames(type_df) <- c("strain", "Type")

type_order <- c(
  "eDCC28","eDCC25","DCC4","eDCC10","DCC2","eDCC9","DCC1","eDCC16",
  "eDCC27","eDCC29","eDCC12","eDCC8","eDCC23","eDCC19","eDCC13",
  "eDCC24","eDCC11","eDCC22","eDCC18","eDCC20","eDCC26","eDCC15",
  "DCC5","eDCC21","eDCC17","eDCC14","NonDCC"
)

cc_dirs <- list.dirs(path = ".", recursive = FALSE)

for (cc in cc_dirs) {
  
  message("Processing ", cc)
  
  matrix_file <- file.path(cc, "matrix.tsv")
  if (!file.exists(matrix_file)) next
  
  df <- read.delim(matrix_file, check.names = FALSE)
  
  mat <- df %>%
    column_to_rownames("target_site") %>%
    as.matrix() %>%
    t() %>%
    as.data.frame()
  
  mat$strain <- rownames(mat)

  mat <- mat %>%
    left_join(type_df, by = "strain")
  
  mat$Type <- factor(mat$Type, levels = type_order)

  df_long <- mat %>%
    pivot_longer(
      cols = -c(strain, Type),
      names_to = "target_site",
      values_to = "value"
    )
  
  df_long$value[df_long$value == 0] <- NA
  
  df_long <- df_long %>%
    arrange(Type, strain)
  
  #plot
  p <- ggplot(
    df_long,
    aes(x = target_site, y = strain, fill = factor(value))
  ) +
    geom_tile(color = NA) +
    scale_fill_manual(
      values = c("1" = "#A50026"),
      na.value = "grey95",
      guide = "none"
    ) +
    facet_grid(
      Type ~ .,
      scales = "free_y",
      space  = "free_y"
    ) +
    theme_minimal(base_size = 5) +
    theme(
      axis.text.x  = element_blank(),
      axis.ticks.x = element_blank(),
      panel.grid   = element_blank(),
      strip.text.y = element_text(angle = 0, size = 8),
      strip.background = element_rect(fill = "grey95", color = NA)
    ) +
    labs(x = "", y = "")
  png(
    filename = file.path(cc, paste0(basename(cc), ".png")),
    width = 12,
    height = 6,
    units = "in",
    bg = "white",
    res = 300
  )
  print(p)
  dev.off()
}

#MAS
library(tidyverse)
type_df <- read.csv("../MAS_type.csv", stringsAsFactors = FALSE)
colnames(type_df) <- c("strain", "Type")

type_order <- c(
  "eDCC33","eDCC37","DCC7","eDCC32","eDCC30","eDCC36",
  "eDCC35","DCC6","eDCC31","DCC3","eDCC34","NonDCC"
)

cc_dirs <- list.dirs(path = ".", recursive = FALSE)

for (cc in cc_dirs) {
  message("Processing ", cc)
  matrix_file <- file.path(cc, "matrix.tsv")
  if (!file.exists(matrix_file)) next
  df <- read.delim(matrix_file, check.names = FALSE)
  mat <- df %>%
    column_to_rownames("target_site") %>%
    as.matrix() %>%
    t() %>%
    as.data.frame()
  
  mat$strain <- rownames(mat)
  mat <- mat %>%
    left_join(type_df, by = "strain")
  mat$Type <- factor(mat$Type, levels = type_order)
  df_long <- mat %>%
    pivot_longer(
      cols = -c(strain, Type),
      names_to = "target_site",
      values_to = "value"
    )
  
  df_long$value[df_long$value == 0] <- NA
  
  df_long <- df_long %>%
    arrange(Type, strain)
  #plot
  p <- ggplot(
    df_long,
    aes(x = target_site, y = strain, fill = factor(value))
  ) +
    geom_tile(color = NA) +
    scale_fill_manual(
      values = c("1" = "#A50026"),
      na.value = "grey95",
      guide = "none"
    ) +
    facet_grid(
      Type ~ .,
      scales = "free_y",
      space  = "free_y"
    ) +
    theme_minimal(base_size = 5) +
    theme(
      axis.text.x  = element_blank(),
      axis.ticks.x = element_blank(),
      panel.grid   = element_blank(),
      strip.text.y = element_text(angle = 0, size = 8),
      strip.background = element_rect(fill = "grey95", color = NA)
    ) +
    labs(x = "", y = "")
  png(
    filename = file.path(cc, paste0(basename(cc), ".png")),
    width = 10,
    height = 3.5,
    units = "in",
    bg = "white",
    res = 300
  )
  print(p)
  dev.off()
}

```

#Unfixed mutations(FigS8)
```{r}
library(tidyverse)
library(ggplot2)
df <- read.csv("all_unfix.csv", header = TRUE)
df <- df %>%
  arrange(desc(count))
df_long <- df %>%
  pivot_longer(
    cols = c(NS, S),
    names_to = "Mutation_Type",
    values_to = "Count"
  )
df_long$target_gene <- factor(df_long$target_gene,
                              levels = df$target_gene)
#plot
ggplot(df_long, aes(x = target_gene, y = Count, fill = Mutation_Type)) +
  geom_bar(stat = "identity", width = 0.7) +
  scale_fill_manual(
    values = c(
      "NS" = "#F2713B",
      "S"  = "#476FB4"
    )) +
  labs(
    x = "Gene",
    y = "Unfixed Mutations"
  ) +
  theme_classic(base_size = 14) +
  theme(
    text = element_text(family = "Arial"),
    axis.text.x = element_text(angle = 60, hjust = 1),
    axis.line = element_line(size = 0.6),
    axis.ticks = element_line(size = 0.6)
  )
```

#Distribution of nonsynonymous mutation counts per isolate(FigS10A-C)
```{r}
#FigS10A-B
library(tidyverse)
library(tidyverse)
library(ggpubr)
library(patchwork)

df <- read.csv("all_mutations_distribution.csv")
df$group <- factor(df$group, levels=c("A","B"))
theme_pnas <- theme_classic(base_size = 14) +
  theme(
    axis.line = element_line(size=0.6),
    axis.ticks = element_line(size=0.6),
    text = element_text(family="Arial"),
    legend.position=""
  )
#plot
plot_group <- function(sub_df){
  ggplot(sub_df, aes(x=count, fill=group)) +
    geom_histogram(binwidth=1, color="black", alpha=0.5, position="identity") +
    geom_density(aes(y=..count..), lwd = 1.2, alpha=0.3, color="black", size=1, adjust=1.6) + 
    scale_fill_manual(values=c("#4DBBD5","#E64B35")) +
    scale_x_continuous(breaks = seq(min(sub_df$count), max(sub_df$count), by=1)) +
    labs(
      x="Mutation count",
      y="Number of isolates",
      fill="Group"
    ) +
    theme_pnas
}

pA <- plot_group(df %>% filter(group=="A"))
pB <- plot_group(df %>% filter(group=="B"))

fig <- pA / pB + plot_annotation(tag_levels="A")
fig

#FigS10C
library(tidyverse)
library(ggpubr)

df <- read.csv("all_mutations_distribution.csv")
df$group <- factor(df$group, levels=c("A","B"))
theme_pnas <- theme_classic(base_size = 14) +
  theme(
    axis.line = element_line(size=0.6),
    axis.ticks = element_line(size=0.6),
    text = element_text(family="Arial"),
    legend.position="top"
  )

#Wilcoxon p
p_val <- wilcox.test(count ~ group, data=df)$p.value
p_val_label <- paste0("p = ", signif(p_val, 3))
#plot
ggplot(df, aes(x=count, fill=group, color=group)) +
  geom_density(aes(y = ..density.. * 100), alpha=0.3, size=1, adjust=1.6) +
  scale_x_continuous(breaks = seq(min(df$count), max(df$count), by=1)) +
  scale_y_continuous(labels = function(x) paste0(round(x,1), "%")) +
  scale_fill_manual(
    values=c("#4DBBD5","#E64B35"),
    labels=c("DCC1-3","Others") 
  ) +
  scale_color_manual(
    values=c("#4DBBD5","#E64B35"),
    labels=c("DCC1-3","Others") 
  ) +
  labs(
    x="Mutation count",
    y="Density",
    fill="Group",
    color="Group"
  ) +
  theme_pnas +
  annotate("text", 
           x = 5, 
           y = 30,  
           label = p_val_label, size=5)

```
